Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex
Results section and table

The information in Table \ref{tbl:data} was captured during the studies, so that we could statistically analyses the features used by the participants.

\begin{table*}[htdp]
\small
\begin{center}
\begin{tabular}{|r|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Participants & 1 &2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20\\
\hline\hline
gender&f&m&f&f&f&f&f&m&f&f&m&f&m&f&m&m&m&m&m&m\\
A condition first task &y&y&y&n&n&y&n&n&y&y&n&n&y&y&n&n&n&n&n&n\\
\hline\hline
A Condition: task &4&2&3&4&3&&2&1&4&1&4&1&3&2&3&2&1&4&3&2\\
paper used&n&n&n&n&n&n&y&n&y&y&n&y&n&n&y&n&n&n&n&n\\
charts used &1&2&2&0&2&4&5&0&0&0&2&3&2&0&0&0&3&3&4&1\\
maps used &1&1&2&2&2&1&1&0&1&0&1&1&2&1&0&1&0&0&2&1\\ 
same as &4&3&3&6&0&2&0&2&1&0&6&5&6&2&7&0&6&7&7&7\\
number data sources  &4&3&4&4&4&3&4&3&4&4&3&3&5&4&5&4&4&5&5&4\\
chosen restaurant/uni &4.1&2.4&3.5&4.3&3.3&&2.4&1.4&4.2&1.6, 1.3, 1.2& 4.2& 1.4, 1.5, 1.3& 3.2& 2.1, 2.3, 2.6& 3.5, 3.3&2.6, 2.3, 2.5&1.6, 1.5, 1.3&4.1&3.3&2.4, 2.5, 2.6\\
\hline\hline
 B Condition:task &3&&4&3&4&2&1&2&2&3&2&3&1&4&1&4&2&2&1&3\\
 paper used &n&n&n&n&n&n&y&n&y&y&n&y&n&y&y&n&n&y&n&n\\
 spreadsheet/website&&&&&&&&&&&&&&&&&&&&\\
 number of spreadsheets used&5/5&4/4&2/5&1.5&2/5&5/5&4/4&2/4&3/4&&2/4&4/5&2/4&4/5&2/4&2/5&4/4&4/4&0&5/5\\
 number of websites used&1&1&4&3&3&0&2&3&2&&1&2&3&1&2&3&2&0&4&0\\
 chosen restaurant/uni&3.5&&4.2&3.3&4.3&2.1&1.4,1.2,1.6&2.1&2.3,2.6,2.5&3.5&2.2,2.3,2.6&3.5&1.1&4.1&1.6&4.2&2.6,2.3, 2.5&2.3,2.5,2.6&1.1, 1.3, 1.4&3.5\\
 \hline
\end{tabular}
\end{center}
\caption{Participants data.} \label{tbl:data}
\normalsize
\end{table*}

@@

In the B conditions, users were given the option of using websites and or a spreadsheet to make their choice.  Participants who opted to use websites to make their decisions repeatedly encountered a number of difficulties and issues. In particular, there was significant confusion over the meaning of data points, for example the percentage-based rankings of university teaching by the Times Higher Education. There were numerous usability issues in using websites, particularly in searching for university courses and course requirements. Similarly, participants found it difficult to understand the locations of restaurants in cities that they were not familiar, and could not find a way to plot the shortlist of restaurants onto the same map using the websites. Overall, the users that spent the most time using websites exhibited significant frustration attempting to locate and compare different criteria (such as course entry requirements, or restaurant locations), and all ended up falling back to using the supplied spreadsheets.

Participants who opted to use the spreadsheet to support their decisions switched between worksheets to view data from different websites.  They used different approaches to using the spreadsheets, some participants were keen to collate all data onto a single sheet, so that they could compare the values all at once. However, this approach was error prone, for example participants noticing too late that the ordering of rows was different on each sheet, so that their pasted values were incorrectly mapped. Others used pen and paper to collate the values, which was often faster and resulted in less observed frustration. While the majority of users did not
attempt anything complex with Excel (in fact only one users used charts), there was some advanced use of Excel observed.
One user explained that they did not like to look at numbers, and so coloured the cells of the types of restaurant, and the
friends' preferences, and matched the colours to make their decision. Another user calculated their own weighted metric
of which university to choose by averaging different metrics supplied by the data sources.

>>>>

The information in Table \ref{tbl:data} was captured during the studies, so that we could statistically analyse the features used by the participants.

\begin{table*}[htdp]
\small
\begin{center}
\begin{tabular}{|r|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|}
\hline
Participants & 1 &2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20\\
\hline\hline
gender&f&m&f&f&f&f&f&m&f&f&m&f&m&f&m&m&m&m&m&m\\
A condition first task &y&y&y&n&n&y&n&n&y&y&n&n&y&y&n&n&n&n&n&n\\
\hline\hline
A Condition: task &4&2&3&4&3&&2&1&4&1&4&1&3&2&3&2&1&4&3&2\\
paper used&n&n&n&n&n&n&y&n&y&y&n&y&n&n&y&n&n&n&n&n\\
charts used &1&2&2&0&2&4&5&0&0&0&2&3&2&0&0&0&3&3&4&1\\
maps used &1&1&2&2&2&1&1&0&1&0&1&1&2&1&0&1&0&0&2&1\\ 
same as &4&3&3&6&0&2&0&2&1&0&6&5&6&2&7&0&6&7&7&7\\
number data sources  &4&3&4&4&4&3&4&3&4&4&3&3&5&4&5&4&4&5&5&4\\
chosen restaurant/uni &4.1&2.4&3.5&4.3&3.3&&2.4&1.4&4.2&1.6, \newline 1.3, \newline 1.2& 4.2& 1.4, \newline 1.5, \newline 1.3& 3.2& 2.1, \newline 2.3, \newline 2.6& 3.5, \newline 3.3&2.6, \newline 2.3, \newline 2.5&1.6, \newline 1.5, \newline 1.3&4.1&3.3&2.4, \newline 2.5, \newline 2.6\\
\hline\hline
 B Condition:task &3&&4&3&4&2&1&2&2&3&2&3&1&4&1&4&2&2&1&3\\
 paper used &n&n&n&n&n&n&y&n&y&y&n&y&n&y&y&n&n&y&n&n\\
 spreadsheet/website&&&&&&&&&&&&&&&&&&&&\\
 number of spreadsheets used&5/5&4/4&2/5&1.5&2/5&5/5&4/4&2/4&3/4&&2/4&4/5&2/4&4/5&2/4&2/5&4/4&4/4&0&5/5\\
 number of websites used&1&1&4&3&3&0&2&3&2&&1&2&3&1&2&3&2&0&4&0\\
 chosen restaurant/uni&3.5&&4.2&3.3&4.3&2.1&1.4, \newline 1.2, \newline 1.6&2.1&2.3, \newline 2.6, \newline 2.5&3.5&2.2, \newline 2.3, \newline 2.6&3.5&1.1&4.1&1.6&4.2&2.6, \newline 2.3, \newline 2.5&2.3, \newline 2.5, \newline 2.6&1.1, \newline 1.3,  \newline 1.4&3.5\\
 \hline
\end{tabular}
\end{center}
\caption{Participants data.} \label{tbl:data}
\normalsize
\end{table*}

@@

In the B conditions, participants were given the option of using websites and or a spreadsheet to make their choice.  Participants who opted to use websites to make their decisions repeatedly encountered a number of difficulties and issues. In particular, there was significant confusion over the meaning of data points, for example the percentage-based rankings of university teaching by the Times Higher Education. There were numerous usability issues in using websites, particularly in searching for university courses and course requirements. Similarly, participants found it difficult to understand the locations of restaurants in cities that they were not familiar, and could not find a way to plot the shortlist of restaurants onto the same map using the websites. Overall, the users that spent the most time using websites exhibited significant frustration attempting to locate and compare different criteria (such as course entry requirements, or restaurant locations), and all ended up falling back to using the supplied spreadsheets.

Participants who opted to use the spreadsheet to support their decisions switched between worksheets to view data from different websites.  They used different approaches to using the spreadsheets, some participants were keen to collate all data onto a single sheet, so that they could compare the values all at once. However, this approach was error prone, for example participants noticing too late that the ordering of rows was different on each sheet, so that their pasted values were incorrectly mapped. Others used pen and paper to collate the values, which was often faster and resulted in less observed frustration. While the majority of users did not
attempt anything complex with Excel (in fact only one user used charts), there was some advanced use of Excel observed.
One user explained that they did not like to look at numbers, and so coloured the cells of the types of restaurant, and the
friends' preferences, and matched the colours to make their decision. Another user calculated their own weighted metric
of which university to choose by averaging different metrics supplied by the data sources.
